### 2010-12-20 Documentation/atropos/atropos.tex
ENH: Bweb evaluation results added.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@708 fd2da0a4-d968-48df-9cb5-d8c496287cbf

\subsection{BrainWeb Evaluation}
\label{sec:bweb} The BrainWeb data is freely available at
\url{http://mouldy.bic.mni.mcgill.ca/brainweb/}.  We employ both the
individual subject data and the BrainWeb20 data in this evaluation.
\subsubsection{Single-Subject Evaluation} We use the single-subject
data with 3\% noise and bias 0, 20 and 40 \% RF inhomogeneity.  We
study the effect of the MRF prior term and initialization strategy on
the Dice overlap between ground truth and the segmentation result for
each tissue.  We test both K-means and prior label image
initialization with MRF $\beta \in \{ 0.00 , 0.05 , 0.10 , 0.15 , 0.20
, 0.25 , 0.30 \}$ at each bias field.  We also feed the white matter
probability map derived from K-means into N4 to guide the bias
correction.  Segmentation is then repeated, with the same parameters,
but with the N4 corrected image as input.  Thus, we are able to
compare the impact of bias on our N4 and Atropos algorithm and also
the validity of our prior label image initialization.  The prior label
image manual initialization was based on a crude ITK-SNAP-based labeling of a
small set of voxels for each tissue.  
\begin{figure}
\begin{center}
\begin{tabular}{c}
% \includegraphics[height=8in]{Figures/final_results_majority_vote_vs_atropos.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small Brainweb single-subject results for
  each tissue.  The results show that the N4 bias correction
  algorithm, combined with Atropos, results in a minimal effect of
  bias, even at the 40\% level.  The optimal $\beta$ for the MRF term
  appears to be between $0.1$ and $0.2$.  The prior label image
  initialization is competitive with but inferior to K-means.}
\label{fig:hammers}
\end{center}
\end{figure}
\subsubsection{20 Subject Evaluation}

>>>>

\subsection{BrainWeb Evaluation}
\label{sec:bweb} The BrainWeb data is freely available at
\url{http://mouldy.bic.mni.mcgill.ca/brainweb/}.  We employ both the
individual subject data and the BrainWeb20 data in this evaluation.
\subsubsection{Single-Subject Evaluation} We use the single-subject
data with 3\% noise and bias 0, 20 and 40 \% RF inhomogeneity.  We
study the effect of the MRF prior term and initialization strategy on
the Dice overlap between ground truth and the segmentation result for
each tissue.  We test both K-means and prior label image
initialization with MRF $\beta \in \{ 0.00 , 0.05 , 0.10 , 0.15 , 0.20
, 0.25 , 0.30 \}$ at each bias field.  We also feed the white matter
probability map derived from K-means into N4 to guide the bias
correction.  Segmentation is then repeated, with the same parameters,
but with the N4 corrected image as input.  The resulting algorithm is
similar to those methods that fix segmentation parameters while
estimating bias and fix bias while estimating segmentation parameters.
Thus, with this simple evaluation, we are able to compare the impact
of bias on our N4 and Atropos algorithm and also the validity of our
prior label image initialization.  The prior label image manual
initialization was based on a crude ITK-SNAP labeling of a small
set of voxels for each tissue.  Results, in terms of
Dice overlap, are shown in figure~\ref{fig:bweb1}.
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_B_RF0.pdf}
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_B_RF20.pdf}
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_B_RF40.pdf}\\
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_N4_RF0.pdf}
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_N4_RF20.pdf}
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_N4_RF40.pdf}\\
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_PLI_RF0.pdf}
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_PLI_RF20.pdf}
\includegraphics[height=2in]{Figures/tissue_dice_vs_mrf_PLI_RF40.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small Brainweb single-subject results for
  each tissue.  The results show that the N4 bias correction
  algorithm, combined with Atropos, results in a minimal effect of
  bias, even at the 40\% level.  The optimal $\beta$ for the MRF term
  appears to be between $0.1$ and $0.2$.  The prior label image
  initialization is competitive with but inferior to K-means.}
\label{fig:bweb1}
\end{center}
\end{figure}
\subsubsection{20 Subject Evaluation}
